\chapter{Testing}

Testing is a critical phase in the development lifecycle designed to ensure that the system meets the predefined requirements and operates reliably. It involves the systematic execution of system functionalities to identify bottlenecks, bugs, and data leakage risks. For an AI-integrated application, testing extends beyond traditional unit scripts to include LLM prompt validation and API resilience checks under load.

\section{Objectives of testing}
The main objectives of our testing phase include:
\begin{enumerate}
    \item To verify that voice-to-code transcription accurately identifies technical keywords.
    \item To ensure rapid responsiveness (low latency) from the Genkit orchestration layer.
    \item To validate that user sessions accurately persist within Firestore across device reloads.
    \item To confirm that memory limits (e.g. 50MB file uploads) are strictly enforced and gracefully fail.
    \item To ensure that the cross-user data isolation mechanisms successfully block unauthorized queries.
    \item To identify UI/UX flaws across varied devices (mobile vs desktop viewports).
    \item To verify the rotational security of JWT sessions provided by Clerk.
\end{enumerate}

\section{Types of testing}

\subsection{1. Unit Testing}
We performed unit testing on the core AI flow logic using Zod for automated schema input validation to ensure that invalid or malformed data never hits the Gemini API.

\subsection{2. Integration Testing}
Integration testing verified the critical interaction between our independent modules, specifically the sync logic between Clerk identity tokens and Firebase custom Auth tokens.

\subsection{3. System testing}
System testing involved full end-to-end testing of the complete, integrated Aether platform on Vercel's edge network to evaluate the system's compliance with its specified requirements.

\subsection{4. Performance testing}
Simulated high-concurrency connections were established to test serverless autoscaling components and confirm that `withRetry` logic correctly handled intermittent 429 Rate Limits from LLM endpoints.

\subsection{5. Security Testing}
A specialized security audit focused on data isolation. Red-team tests simulated malicious users attempting to craft custom network requests to access alternative `UID` protected sub-collections.

\section{Test cases}

\subsection{1. user side}
\begin{table}[h!]
\centering
\begin{tabular}{|l|p{4cm}|p{4cm}|c|}
\hline
\textbf{Test ID} & \textbf{User Action} & \textbf{Expected System Output} & \textbf{Status} \\ \hline
TC-U1 & User attempts to login without registering & Rejection with explicit ``User Not Found'' toast & Pass \\ \hline
TC-U2 & User inputs voice command with heavy background noise & Transcription engine filters noise; AI generates close-match intent & Pass \\ \hline
TC-U3 & User uploads a 70MB corrupt PDF & UI blocks upload with ``File Exceeds Limits'' message immediately & Pass \\ \hline
TC-U4 & User modifies URL to fetch `session/123` lacking owner tag & Firebase Rules block request, UI triggers redirect to Dashboard & Pass \\ \hline
\end{tabular}
\caption{User-Facing Boundary Test Cases}
\end{table}

\section{Bug report}
During initial QA cycles, several non-critical UI tracking bugs were discovered:
\begin{itemize}
    \item \textbf{Bug-001}: The chat auto-scroll failed to engage when large code blocks pushed the viewport bounds rapidly. (Fixed via React Ref mutation observer).
    \item \textbf{Bug-002}: Dark mode toggle flashed white for 100ms before persisting during initial Next.js hydration. (Fixed with inline script injector technique).
    \item \textbf{Bug-003}: `withRetry` delay timer occasionally exceeded the Vercel Serverless Function 10-second timeout. (Fixed by capping maximum retries to 2 attempts).
\end{itemize}

\section{Test Result Summary}
The multi-layered testing strategy confirms that Aether Co-Pilot is not only functionally accurate but also resilient against common web vulnerabilities. Specifically, all 35 core Genkit flows passed their localized evaluations, and zero unauthorized data access leaks were achievable during security penetration rounds. The system comfortably scales up to 100 concurrent inference sessions with minimal latency degradation.

\newpage
