\chapter{Bibliography}

% Setting 1.5 line spacing for bibliography
\setstretch{1.5}

\begin{enumerate}
    \item[1] G. K. Patnaik and M. M. Gore, \textit{``Design of Compiler for Mobile Environment and it’s formalization using Evolving Algebra''}, proceedings of 3rd IEEE International Conference on Mobile Data Management, Singapore, January 2002, PP 159-160.
    \item[2] Vaswani, A., et al., \textit{``Attention Is All You Need''}, Advances in Neural Information Processing Systems, 2017.
    \item[3] Vercel, \textit{``Next.js 15: The Power of Turbopack and React Server Components''}, official documentation, 2024. \url{https://nextjs.org/docs}
    \item[4] Google Cloud, \textit{``Generative AI with Google Cloud and Gemini Flash''}, technical whitepaper, 2024.
    \item[5] Firebase Team, \textit{``Scalability and Security in NoSQL Environments''}, Google Developers Blog. \url{https://firebase.google.com/docs/firestore}
    \item[6] Clerk, \textit{``Modern Identity Management for Next.js 15''}, developer documentation. \url{https://clerk.com/docs}
    \item[7] Resig, J. and Bibeault, B., \textit{``Secrets of the JavaScript Ninja''}, Manning Publications, 2nd Edition.
    \item[8] Zikas, D., \textit{``The Evolution of TypeScript: From Static Typing to AI Schema Safety''}, JSConf, 2023.
    \item[9] OpenAI, \textit{``GPTS and the Future of AI Agents''}, technical report, 2023.
    \item[10] Lewis, P., et al., \textit{``Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks''}, 2020.
    \item[11] Nielsen, J., \textit{``10 Usability Heuristics for User Interface Design''}, Nielsen Norman Group.
    \item[12] Field, R., \textit{``Developing Progressive Web Apps (PWAs) with React''}, O'Reilly Media.
    \item[13] Martin, R. C., \textit{``Clean Code: A Handbook of Agile Software Craftsmanship''}, Prentice Hall.
    \item[14] Radix UI team, \textit{``Accessible UI Components with Radix Primitives''}, \url{https://www.radix-ui.com/}
    \item[15] Tailwind CSS, \textit{``Utility-First CSS: Evolution of Styling''}, \url{https://tailwindcss.com/docs}
    \item[16] Zod developers, \textit{``TypeScript-first Schema Validation with Zod''}, \url{https://zod.dev/}
    \item[17] Genkit authors, \textit{``AI-as-Code: The Genkit Manifesto''}, \url{https://firebase.google.com/docs/genkit}
    \item[18] React 19 team, \textit{``What's New in React 19 and Server Actions''}, official blog post.
    \item[19] Lucide contributors, \textit{``Designing Consistent Icon Systems for Web Apps''}, \url{https://lucide.dev/}
    \item[20] Vercel, \textit{``The Economics of Serverless Deployment''}, technical report.
    \item[21] Fowler, M., \textit{``Refactoring: Improving the Design of Existing Code''}, Addison-Wesley.
    \item[22] Gamma, E., et al., \textit{``Design Patterns: Elements of Reusable Object-Oriented Software''}, Addison-Wesley.
    \item[23] Google AI Studio, \textit{``Gemini 2.0 Flash: Efficiency and Speed at Scale''}, 2024.
    \item[24] World Wide Web Consortium (W3C), \textit{``Web Speech API Specification''}, \url{https://www.w3.org/TR/speech-api/}
    \item[25] MDN Web Docs, \textit{``Using the Web Speech API''}, Mozilla Developer Network.
    \item[26] Burner, J., \textit{``NoSQL Databases: A Survey and Comparison''}, ACM Computing Surveys.
    \item[27] Shore, J., \textit{``The Art of Agile Development''}, O'Reilly Media.
    \item[28] Meyer, B., \textit{``Object-Oriented Software Construction''}, Prentice Hall.
    \item[29] Knuth, D. E., \textit{``The Art of Computer Programming''}, Addison-Wesley.
    \item[30] IEEE Computer Society, \textit{``Software Engineering Body of Knowledge (SWEBOK)''}, IEEE.
    \item[31] Vercel Documentation. (2024). \textit{Next.js 15: The Future of React Frameworks}. Available at: \url{https://nextjs.org/docs}.
    \item[32] Google Cloud. (2024). \textit{Genkit: AI-as-Code for Modern Developers}. Technical Whitepaper.
    \item[33] Radix UI. (2023). \textit{Accessible Design Systems for Modern Web Apps}.
    \item[34] Shneiderman, B. (2022). \textit{Human-Centered AI: A Framework for Design}. Oxford University Press.
    \item[35] Marcus, G., \& Davis, E. (2019). \textit{Rebooting AI: Building Artificial Intelligence We Can Trust}. Pantheon.
    \item[36] Russell, S., \& Norvig, P. (2020). \textit{Artificial Intelligence: A Modern Approach}. 4th Edition. Pearson.
    \item[37] Clerk Auth. (2024). \textit{Identity Management at the Edge}. Engineering Blog.
    \item[38] Firebase Firestore Documentation. (2024). \textit{Security Rules and Path-Driven Authorization}.
    \item[39] React Core Team. (2024). \textit{React 19: Concurrent Rendering and Server Actions}.
    \item[40] OpenAI. (2023). \textit{GPT-4 Technical Report}.
\end{enumerate}

\newpage
